\documentclass[]{article}
\usepackage{setspace}

\begin{document}

\title{Prisoner's Dilemma}
\tableofcontents
\newpage

\begin{spacing}{0.7}


\section{Introduction}
	\subsection{Problem Identification}
		What is the exact problem I want to cover in my MA?
	\subsection{Problem Delimitation}
		How can I narrow down my problem so that it corresponds to the scope of the Maturaarbeit but still provides interesting insights.
	\subsection{Objective and Approach}
	What do I want to achieve in this MA and how do I accomplish this?

\section{Theoretical Foundations}
	\subsection{Game Theory}
		What is Game Theory?
	\subsection{Prisoner's Dilemma}
		What is the Prisoner's Dilemma?
	\subsection{Advanced Variants}
		What variants of the Prisoner's Dilemma already have been developed?
	\subsection{Current Findings}
		What has been found out about the Prisoner's Dilemma?
	\subsection{Relevance to the Project}
		In what way are these findings relevant to my project?
		

\section{Methods and Implementation}
	\subsection{Programming Language}
		What programming language am I going to use?
	\subsection{Programme Structure}
		How is the simulation going to be structured?
	\subsection{Data Generation}
		What data is going to be generated?
	\subsection{Implemented Variants}
		Which variants am I going to implement?
		How can I modify the existing variants to get new insights?
	\subsection{Simulated Strategies}
		What strategies am I going to develop?
	
\section{Results}
	\subsection{Variant 1 (Iterated)}
	\subsection{Variant 2 (Continuous)}
	\subsection{Variant 3 (Evolution)}

\section{Discussion}
	What insight does this raw data provide? \rightarrow interpretation

\section{Conclusions and Outlook}
	\subsection{Summary and Quintessence}
		Can we learn something about these interpretations/insights?
	\subsection{Application in the Real World}
		Can I apply these insights to the real world?

\section{Self Reflection}
	\subsection{Challenges}
		What was challenging?
	\subsection{Learnings}
		What have I learned?

\section{Annex}

\end{spacing}

\end{document}
